Usable Security in Virtual Power Plants

### 2018-01-24 acmart-master/draft.tex
Suggestion based changes

Critical infrastructures are integral to the functioning of our daily lives. They are changing in order to solve different problems it faces nowadays. The growth of power demand, integration of markets and the need of sustainable and efficient energy sources. \\
One such important critical infrastructure is the energy grid. A typical energy grid is divided into several domains such as generation, transmission and distribution. All the actors within domains of a energy grid are connected through information and communication technology(ICT). Hence, energy grids have continuously been the target of cyber attacks and provided their use of standard architecture and internet, they are relatively easier to attack. Security mechanisms have been introduced to protect against such attacks. Security-by-design approach has been used to determine security measures for various systems during design phase. With this approach, the system is equipped to deal with difficult scenarios before deployment. \\ However, there may be instances where the user must intervene to control the system when under attack and stress. During such instances, the user maybe asked to re-authenticate themselves, at which point remembering increasingly difficult passwords and entering it %correctly actually causes an overhead on the user. The security mechanism in fact is a hindrance here. Such a situation could be avoided if the authentication system in place is usable under different conditions.
%Intro big pic, narrow, Related work seperate subsection

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model using security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems\cite{nurse2011guidelines}. Standards such as ISO 9241-11\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system. A first look at such a relation is provided\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase\cite{nielsen1992usability}.

@@

\begin{figure}[H]
\caption{Usability Framework. Source: \cite{bevan1995human}}
\label{fig:usability1}
\includegraphics[scale=0.2]{img/usability1.png}
\end{figure}

@@

\begin{figure}[H]
\caption{Quality Plan. Source: \cite{bevan1995human}}
\label{fig:usability2}
\includegraphics[scale=0.2]{img/usability2.png}
\end{figure}

>>>>

Critical infrastructures are integral to the functioning of our daily lives. They are changing in order to solve different problems it faces nowadays. The growth of power demand, integration of markets and the need of sustainable and efficient energy sources. \\
One such important critical infrastructure is the energy grid. A typical energy grid is divided into several domains such as generation, transmission and distribution. All the actors within domains of a energy grid are connected through information and communication technology(ICT). Hence, energy grids have continuously been the target of cyber attacks and provided their use of standard architecture and internet, they are relatively easier to attack. Security mechanisms have been introduced to protect against such attacks. Security-by-design approach has been used to determine security measures for various systems during design phase. With this approach, the system is equipped to deal with difficult scenarios before deployment. \\ However, there may be instances where the user must intervene to control the system when under attack and stress. During such instances, the user maybe asked to re-authenticate themselves, at which point remembering increasingly difficult passwords and entering it correctly actually causes an overhead on the user. The security mechanism in fact is a hindrance here. Such a situation could be avoided if the authentication system in place is usable under different conditions.
%Intro big pic, narrow, Related work seperate subsection

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model using security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems\cite{nurse2011guidelines}. Standards such as ISO 9241-11\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system. A first look at such a relation is provided\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase\cite{nielsen1992usability}. The goal of this research to establish how usability of security in power plants can be achieved. A second goal is to reduce the burden on a power plant operator, since operation of a plant can be stressful. We assume that the operator of the power plant is oblivious to the security design. We shall focus only on security and usability and their relation. Hence, usability of other systems are not considered. Only systems having an user interface are considered.

@@

\begin{figure}[H]
\caption{Usability Framework. Source: \cite{bevan1995human}}
\label{fig:usability1}
\includegraphics[scale=0.285]{img/usability1.png}
\end{figure}

@@

\begin{figure}[H]
\caption{Quality Plan. Source: \cite{bevan1995human}}
\label{fig:usability2}
\includegraphics[scale=0.3]{img/usability2.png}
\end{figure}
